### 2020-03-11 report/05-stability.Rmd
Recompute biomass correlation between trophic group + plot results
No link between stability and strength of bottom-up effect

```{r}
#TODO: Update cor_troph_group 
myload(cor_troph_group, dir = mypath("data"))
cor_troph_group %>%
  left_join(hab_type, by = "station") %>%
  filter(!is.na(hab_type)) %>%
  ggplot(aes(x = hab_type, y = cor_troph)) +
  geom_boxplot() 
```

>>>>

## Temporal correlation between troph group biomass

```{r}
#TODO: Update cor_troph_group 
myload(cor_troph, dir = mypath("data"))
cor_troph %>%
  left_join(stab_div_troph, by = "station") %>%
  ggplot(aes(y = log10(1/ biomass_cv), x = cor_troph, color = troph_group)) +
  geom_point()

cor_troph %>%
  left_join(stab_div_troph, by = "station") %>%
  ggplot(aes(y = cor_troph, x = log10(richness_tot), color = troph_group)) +
  geom_point()
```
